Hypertension and microbiome

### 2019-06-03 articletwo.Rmd
Pcoa loading

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(xtable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
library(RColorBrewer)
library(gvlma)
```

@@

pcoa.df %>% pull(HYPERTENSION) %>% summary

@@

@@

@@

@@

>>>>

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(xtable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
library(RColorBrewer)
library(gvlma)
library(purrr)
```

@@

@@

```{r top generas, eval = FALSE, include = FALSE}
abund.genus <- abundances(pseq.genus, transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))

abund.genus.bacteria <- colnames(abund.genus)[-1] %>% mygrep(".bacteria$", .)

pcoacorabund <- function(names, pcoa) {
    lapply(c2l(abund.genus.bacteria), function (name) 
                     lapply(c2l(1,2,3), function(index) {
                             model <- lm(abund.genus[,name] ~ pcoa[,index])
                             summary(model)$r.squared
                         }))
}

pcoacor.genus <- pcoacorabund(abund.genus.bacteria, pcoa.vectors)
pcoacor.genus.df <- map_df(pcoacor.genus, ~as.data.frame(.x), .id="id")

pcoacor.genus.df %>%
    arrange(-X3) %>%
    head(10) %>% kable
```

@@

```{r pcoa 3d}
theta <- 130
phi <- 10
pcoa3d.plot <- ggplot(data=pcoa.df, aes(x=Axis.1, y = Axis.2, z=Axis.3, color = HYPERTENSION)) +
  axes_3D(theta=theta, phi=phi) +
  stat_3D(theta=theta, phi=phi, size = 0.01, alpha=0.4) +
  labs_3D(theta=theta, phi=phi, 
          hjust=c(1,0,0), vjust=c(1.5,1,-.2),
          labs=c(sprintf("PCoA Axis 1 (%.1f%%)", 100*eig.fracs[1]),
                 sprintf("PCoA Axis 2 (%.1f%%)", 100*eig.fracs[2]),
                 sprintf("PCoA Axis 3 (%.1f%%)", 100*eig.fracs[3]))) #+
#  theme_void()

ggsave(file = "cache/pcoa-species-3d.png", plot=pcoa3d.plot, height=4, width=7, units = "in", dpi = 300)

@@

Catabacter, Robinsoniella

```{r compare maaslin to sun, eval = FALSE}
maas.results.df.all <- maaslin$genus %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  Feature = gsub("_Bacteria", "", Feature),
                  beta = Coefficient)

maas.results.df.all %>% pull(Feature) %>% sort %>% unique %>% mygrep("Robin", .)

genus.taxa <- pseq.genus.core %>% abundances %>% rownames

genus.taxa %>% mygrep("Catabacter", .)

maaslin.test <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE",
                                               "HYPERTENSION"),
                                    forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                                               "DIAB", "BL_USE_RX_C03",
                                               "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                               taxa = paste(c("Faecalicatena.Bacteria",
                                        "Catabacter.Bacteria",
                                        "Robinsoniella.Bacteria"), collapse = ", "))

@@

```{r squared clinical, eval = FALSE, include = FALSE}
mylmrsqr <- function(df, response, loopcovariates) {
    model.list <- list()
    for (i in seq(length(loopcovariates))) {
        fo <- sprintf("%s ~ %s", response, paste(loopcovariates, collapse = " + "))
        message(sprintf("formula : %s", fo))
        model <- lm(as.formula(fo), data = df)
        model$call <- as.formula(fo)
        model.list[[i]] <- model
        loopcovariates <- loopcovariates[-length(loopcovariates)]
    }
    return(model.list)
}

af.models <- mylmrsqr(df = meta(pseq.species),
         response = "MAP",
         loopcovariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB",
                            "ANYDRUG"))

af <- do.call(anova, af.models)

af %>%
    as.data.frame %>%
        mutate(Rsqr =  `Sum of Sq`/sum(`Sum of Sq`, na.rm = T)*100)

c(summary(lm(SYSTM ~ BL_AGE + SEX, meta(pseq.species)))$adj.r.squared,
summary(lm(DIASM ~ BL_AGE + SEX, meta(pseq.species)))$adj.r.squared,
summary(lm(PULSEPRESSURE ~ BL_AGE + SEX, meta(pseq.species)))$adj.r.squared,
summary(lm(MAP ~ BL_AGE + SEX, meta(pseq.species)))$adj.r.squared) %>% mean

c(summary(lm(SYSTM ~ BL_AGE + SEX + BMI, meta(pseq.species)))$adj.r.squared,
summary(lm(DIASM ~ BL_AGE + SEX + BMI, meta(pseq.species)))$adj.r.squared,
summary(lm(PULSEPRESSURE ~ BL_AGE + SEX + BMI, meta(pseq.species)))$adj.r.squared,
summary(lm(MAP ~ BL_AGE + SEX + BMI, meta(pseq.species)))$adj.r.squared) %>% sort
